Higher-Order unification for free!

### 2024-04-16 paper/main.tex
lemma 5.13

% \noteD[inline]{Below the proof of \cref{prop:w-preservation}, ho usato 3 lemmi ausiliari,
% forse si può compattare in una prova più piccola?}
\begin{lemma}
  Given a \linketa \linketaM{\Gamma}{X}{T}, the unification done by \progressetaleft is between
  terms in $\wellb$  
  \label{lemma:unif-eta-1}
\end{lemma}

\begin{proof}[Proof sketch]
  Let $\sigma$ be the substitution, such that $\wellb(\sigma X)$ (since \Ue preserves \wellb),
  By\todo{reformulate}
  \progressetaleft, if 1) the $\sigma X$ is a name, a constant or an
  application, then, $\lambda x.X \appsep x$ is unified with the \rhs. By
  \cref{inv:link-eta-right} and \cref{lemma:unif-eta-aux},
  $\rhs = \lambda x. t$ and $\wellb(t)$.
  Otherwise, 2) $\sigma X = \lambda x.t$.
  % \todo{what does as a functor mean?}
  In both cases, unification is
  performed between terms in \wellb.
\end{proof}

>>>>

% \noteD[inline]{Below the proof of \cref{prop:w-preservation}, ho usato 3 lemmi ausiliari,
% forse si può compattare in una prova più piccola?}
\begin{lemma}
  Given a \linketa \linketaM{\Gamma}{X}{\lambda x.t}, the unification done by \progressetaleft is between
  terms in $\wellb$  
  \label{lemma:unif-eta-1}
\end{lemma}

\begin{proof}[Proof sketch]
  Let $\sigma$ be the substitution, such that $\wellb(\sigma X)$ (since \Ue preserves \wellb).
  By \cref{inv:link-eta-right}, we have $\wellb(t)$.
  If $\sigma X = \lambda x.r$, then $r$ is unified with $t$: both terms are \wellb.
  Otherwise, $\lambda x. X x$ is unified with $\lambda x. t$, and $X x$ and $t$
  are both \wellb. This concludes the proof.
\end{proof}
